|

### 2022-07-24 manuscript.Rmd
comment out in_header: cannot render

bibliography: ["bib/references.bib", "bib/packages.bib"]
output:
  rticles::jds_article: 
    includes:
      in_header: header.tex #header-hidden.tex can be used when creating an anonymized version for review
  bookdown::pdf_book:
    base_format: rticles::jds_article # for using bookdown features like \@ref()
---

>>>>

bibliography: ["bib/references.bib", "bib/packages.bib"]
output:
  rticles::jds_article: 
    # includes:
      # in_header: header.tex #header-hidden.tex can be used when creating an anonymized version for review
  bookdown::pdf_book:
    base_format: rticles::jds_article # for using bookdown features like \@ref()
---
